Below are the .java files used in the implementation of the prototype. These files alone are not enough to compile the prototype from scratch as certain minor things like layouts or manifest files are missing. These and all other files necessary to build the project are present in the source repositories. The repository for the Tomcat portion of the project is located at \url{https://github.com/jorgebv/thesis_tomcat/}. The repository for the Android portion of the project is located at \url{https://github.com/jorgebv/thesis_android/}.

There may appear to be duplicates of certain classes in Appendix A and Appendix B. This is due to minor differences between the versions running on Tomcat server instances, and the versions running on Android hardware. Although some files may contain no changes, all files are included below for the sake of completeness.

The prototype makes use of the Apache HttpComponents library version 4.2.5, which can be found here at the time of writing: \url{http://hc.apache.org/downloads.cgi}. These components are licensed under the Apache License, Version 2.0, a full copy of which can be found here: \url{http://www.apache.org/licenses/LICENSE-2.0.html} as well as within the project source directories.

Many of the files below contain references to a library named ``jorgecastle''. The ``jorgecastle'' library is a minimally modified version of the Bouncy Castle 1.48 release, which can be found here at the time of writing: \url{http://www.bouncycastle.org/latest_releases.html}. All that was changed from the stock Bouncy Castle 1.48 release was the renaming of packages to avoid conflicts with outdated Bouncy Castle versions included in Android, and renaming of the Bouncy Castle provider from ``BC'' to ``JC''. This code is not available due to the large size and trivial nature of the changes. These components are licensed under an adaptation of the MIT X11 License, a full copy of which can be found here: \url{http://www.bouncycastle.org/license.html} as well as within the project source directories.